Thread Pool in GeckoDB/BOLSTER - Integrating a Thread Pool into a high performance Database System \\

### 2018-06-04 Presentations/Paper/paper_thread_pool.tex
Add more figures to paper

@@

\subsection{Enqueueing Tasks}
\begin{figure}
	\includegraphics[width=0.5\textwidth]{img/pool_queue.png}
	\caption{Workflow of task enqueueing and execution in the thread pool}
	\label{fig}
\end{figure}

\subsection{Waiting for Tasks}
As mentioned in the previous section, ids are assigned to the tasks before they are enqueued. 
\subsection{Thread metrics}

@@

\section{Conclusion and Future Work}

\bibliographystyle{splncs}
\bibliography{paper_thread_pool}

>>>>

\begin{figure*}[htbp]
	\includegraphics[width=1.0\textwidth]{img/pool_structure.png}
	\caption{Design of the thread pool system}
	\label{fig0}
\end{figure*}

@@

\subsection{Enqueueing Tasks}
\begin{figure}
	\includegraphics[width=0.5\textwidth]{img/pool_queue.png}
	\caption{Workflow of task enqueueing and execution in the thread pool}
	\label{fig1}
\end{figure}

\subsection{Waiting for Tasks}
\begin{figure}
	\includegraphics[width=0.5\textwidth]{img/waitingconcept.png}
	\caption{Concept of waiting for tasks using a slotmap}
	\label{fig2}
\end{figure}
As mentioned in the previous section, ids are assigned to the tasks before they are enqueued. 
\subsection{Thread metrics}

@@

\section{Conclusion and Future Work}
\cite{pyarali2001evaluating}
\bibliographystyle{splncs}
\bibliography{paper_thread_pool}
